### 2023-09-02 sections/4-results.tex
complexity
results table

Figure [ADD FIGURE NUMBER] is a violin plot which shows the performance of our algorithms
on [ADD DATASET] under [ADD DISTANCE FUNCTION] distance, using [ADD NUMBER OF SHARDS] shards.
On the horizontal axis, we have each of the $k$-NN algorithms described in Section 2.4, as well as  
an additional "algorithm" which we call "Oracle $\rho$-NN" [REPLACE WITH ACTUAL NAME].  With "Oracle $\rho$-NN", we perform $\rho$-NN search using the 
distance to the $k$-th nearest neighbor as the radius. Of course, as it is impossible to
to know the distance to the $k$-th nearest neighbor \emph{a priori}, this algorithm 
is useful only for benchmarking purposes.

@@

>>>>

Figure [ADD FIGURE NUMBER] is a violin plot which shows the performance of our algorithms
on [ADD DATASET] under [ADD DISTANCE FUNCTION] distance, using [ADD NUMBER OF SHARDS] shards.
As indicated in the title, the dataset has cardinality [ADD cardinality] and dimensionality [ADD DIMENSIONALITY].
On the horizontal axis, we have each of the $k$-NN algorithms described in Section 2.4, as well as  
an additional "algorithm" which we call "Oracle $\rho$-NN" [REPLACE WITH ACTUAL NAME].  With "Oracle $\rho$-NN", we perform $\rho$-NN search using the 
distance to the $k$-th nearest neighbor as the radius. Of course, as it is impossible to
to know the distance to the $k$-th nearest neighbor \emph{a priori}, this algorithm 
is useful only for benchmarking purposes.

@@

("deep-image", "cosine"),       // 0
("fashion-mnist", "euclidean"), // 1
("gist", "euclidean"),          // 2
("glove-25", "cosine"),         // 3
("glove-50", "cosine"),         // 4
("glove-100", "cosine"),        // 5
("glove-200", "cosine"),        // 6
("kosarak", "jaccard"),         // 7
("mnist", "euclidean"),         // 8
("nytimes", "cosine"),          // 9
("sift", "euclidean"),          // 10
("lastfm", "cosine"),           // 11

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Performance (ROC AUC) of CHAODA vs. other methods on the 18 test datasets.}
    \label{table:results:test-performance}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
    \textbf{Dataset} & \textbf{Dist.}  &\textbf{Card.}  & \textbf{Dim.}  & \textbf{k}  & \multicolumn{2}{r}\textbf{faiss-ivf} & \multicolumn{2}{r}\textbf{redisearch} & \multicolumn{2}{r}\textbf{hnsw(faiss)} & \multicolumn{2}{r}\textbf{CAKES} \\
    &                &                  &                   &               &             Recall & QPS                           & Recall & QPS                           & Recall & QPS                                           & Recall & QPS \\
    \hline
    nytimes          & cos              & 290,000            & 256             & 10         & 0.69 &  1413.35                       & 0.90 & 616.21                            & 0.97 & 92.92                                         & 1.00 & 42 \\
    \hline
    nytimes          & cos              & 290,000            & 256             & 100        & 0.61 &  0.71                          & 0.50 & 0.45                              & 0.00 & 0.00                                          & 1.00 & 42 \\
    \hline
    fashion-mnist    & euc              & 60,000	         & 784            & 10         & 0.54 & 324.79                           & 0.99 & 444.89                                  & 0.94 & 60.89                                                    & 1.00 & 42 \\
    \hline
    fashion-mnist    & euc              & 60,000             & 784            & 100        & 1.00 & 111.47                           & 0.50 & 0.49                                  & 0.99 & 277.80                                                    & 1.00 & 42 \\
    \hline 
    gist             & euc              & 1,000,000          & 960             & 10         & 1.00 & 3.55                           & -- & --                                     & 0.95 & 149.58                                                   & 1.00 & 42 \\
    \hline
    gist             & euc              & 1,000,000          & 960             & 100        & 1.00 & 2.70                           & 0.68 & 0.47                                 & 0.99 & 59.71                                                    & 1.00 & 42 \\
    \hline
    glove-25         & cos              & 1,183,514          & 25             & 10         & 1.00 & 78.78                          & 1.00 & 37.85                               & 1.00 & 552.67                                                  & 1.00 & 42 \\
    \hline
    glove-25         & cos              & 1,183,514          & 25             & 100        & -- & --                           & -- & --                                & -- & --                                                    & 1.00 & 42 \\
    \hline
    glove-100        & cos              & 1,183,514          & 100            & 10         & 1.00 & 21.16                          & 0.99 & 133.05                                & 0.99 & 155.90                                                  & 1.00 & 42 \\
    \hline
    glove-100        & cos              & 1,183,514          & 100            & 100        & 0.99 &  19.04                          & -- & --                                  & 0.99 & 92.58                                                    & 1.00 & 42 \\
    \hline
    sift             & euc              & 1,000,000          & 128            & 10         & 1.00 &  24.52                          & 1.00 & 505.79                               & 1.00 & 275.07                                                    & 1.00 & 42 \\
    \hline
    sift             & euc              & 1,000,000          & 128            & 100        & 1.00 &  23.50                          & 0.50 & 0.45                                  & 0.99 & 179.14                                                    & 1.00 & 42 \\
    \hline
    deep-image       & cos              & 9,990,000	         & 96             & 10          & 0.00 & 0.00                           & 0.00 & 0.00                                 & 0.00 & 0.00                                                     & 1.00 & 42 \\
    \hline
    deep-image       & cos              & 9,990,000	         & 96             & 100         & 0.00 & 0.00                           & 0.00 & 0.00                                & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    mnist            & euc              & 60,000             & 784             & 10          & 0.00 & 0.00                          & 0.00 & 0.00                                 & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    mnist            & euc              & 60,000             & 784             & 100         & 0.00 & 0.00                          & 0.00 & 0.00                                  & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    glove-50         & cos              & 1,183,514          & 50             & 10          & 0.00 & 0.00                           & 0.00 & 0.00                              & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    glove-50         & cos              & 1,183,514          & 50             & 100         & 0.00 & 0.00                           & 0.00 & 0.00                              & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    lastfm           & cos              & 292,385            & 65             & 10          & 0.00 & 0.00                           & 0.00 & 0.00                               & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    lastfm           & cos              & 292,385            & 65             & 100         & 0.00 & 0.00                           & 0.00 & 0.00                             & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table*}
